A Novel Model-Free Actor-Critic Reinforcement Learning Approach for Dynamic Target Tracking

### 2020-07-10 paperMIC2020/paperIEEE-MIC2020-V1.tex
review

\begin{abstract}
  %
  Addressing the trajectory tracking problem of a mobile robot in tracking a
  dynamic target is still one of the challenging problems in the field of
  robotics. In this paper, we address the position tracking problem of a mobile
  robot where it is supposed to track the position of an mobile target whose
  dynamics is unknown a priori. This problem is even more challenging when the
  dynamics of the mobile robot is also assumed to be unknown, which is indeed a
  realistic assumption. Most of the trajectory tracking solutions proposed in the
  literature in the field of mobile robotics are either focused on algorithms
  that rely on mathematical models of the robots or driven by a overwhelming
  degree of computational complexity. This paper proposes a model-free
  actor-critic reinforcement learning strategy to determine appropriate actuator
  commands for the robot to track the position of the target. We emphasize that
  mathematical models of both mobile robot and the target are not required in
  the current approach. Moreover, Bellman's principle of optimality is utilized
  to minimize the energy required for the robot to track the target. The
  performance of the proposed actor-critic reinforcement learning approach is
  backed by a set of computer experiments with various complexities using a
  virtual circular-shaped mobile robot and a point target modeled by an
  integrator.
%
\end{abstract}

>>>>

\begin{abstract}
  %
  Addressing the trajectory tracking problem of a mobile robot in tracking a
  dynamic target is still one of the challenging problems in the field of
  robotics. In this paper, we address the position tracking problem of a mobile
  robot where it is supposed to track the position of a mobile target whose
  dynamics is unknown a priori. This problem is even more challenging when the
  dynamics of the mobile robot is also assumed to be unknown, which is indeed a
  realistic assumption. Most of the trajectory tracking solutions proposed in the
  literature in the field of mobile robotics are either focused on algorithms
  that rely on mathematical models of the robots or driven by a overwhelming
  degree of computational complexity. This paper proposes a model-free
  actor-critic reinforcement learning strategy to determine appropriate actuator
  commands for the robot to track the position of the target. We emphasize that
  mathematical models of both mobile robot and the target are not required in
  the current approach. Moreover, Bellman's principle of optimality is utilized
  to minimize the energy required for the robot to track the target. The
  performance of the proposed actor-critic reinforcement learning approach is
  backed by a set of computer experiments with various complexities using a
  virtual circular-shaped mobile robot and a point target modeled by an
  integrator.
%
\end{abstract}
